Stream of Consciousness Literature: A 'Joyceless' Linguistic Landscape

### 2024-04-25 paper/paper.qmd
final paper updates

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-word-networks
#| layout-ncol: 2
#| fig-cap: "Word Networks Measured by Frequency and Correlation when Combining All Stream of Consciousness Texts"
#| fig-subcap: ["250 Frequency, 0.2 Correlation", "300 Frequency, 0.4 Correlation", "350 Frequency, 0.6 Correlation", "400 Frequency, 0.8 Correlation"]

>>>>

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-word-networks
#| layout-ncol: 2
#| fig-cap: "Word Networks Measured by Frequency and Correlation when Combining All SOC Texts"
#| fig-subcap: ["250 Frequency, 0.2 Correlation", "300 Frequency, 0.4 Correlation", "350 Frequency, 0.6 Correlation", "400 Frequency, 0.8 Correlation"]
